Effects of sexual selection on non-sexual fitness components: a meta-analysis

### 2018-03-01 meta_analysis_sexual_selection_pop_fitness.Rmd
Spellingz
1/3 Post meeting update

```{r warning=FALSE, message=FALSE, results='hide'}
library(knitr)
library(pander)
library(compute.es)
library(metafor)
library(dplyr)
library(lme4)
library(forestplot)
library(ggplot2)
library(MuMIn)
library(glmulti)
library(cowplot)
library(ggrepel)
library(reshape2)
library(RColorBrewer)
source("Vdodge_function.R") # nice function for ggplot
```

@@

**Table S1:** WRITE TABLE LEGEND.
 <br/><br/> 
<input type=button class=hideshow></input>
```{r}
Eligibility.criteria <- read.csv('data/Eligibility Workbook(22.02).csv', 
                                 fileEncoding="UTF-8")
Eligibility.criteria %>% 
  pander(split.cell = 40, split.table = Inf)
```

@@

**Table S2:** Table of effect sizes included in our meta-analysis. See the text following the table for an explanation of each column.
 <br/><br/> 
<input type=button class=hideshow></input>
```{r}
# Load the data and clean up the variable formats
prelim.data <- read.csv('data/Preliminary data frame 22.2.18.csv')
prelim.data$Study.ID <- prelim.data$Study.ID %>% factor()
prelim.data$Taxon <- prelim.data$Taxon %>% factor()
prelim.data$Group.ID <- prelim.data$Group.ID %>% factor()
prelim.data$Authors <- prelim.data$Authors %>% factor()
prelim.data$Environment <- prelim.data$Environment %>% factor %>% relevel(ref="Unstressed")
prelim.data$Sex <- prelim.data$Sex %>% factor %>% relevel(ref="B")
prelim.data$Ambiguous <- prelim.data$Ambiguous %>% factor()
prelim.data$Species <- prelim.data$Species %>% factor()
#Outcome.Class.2 is using the categories that were decided by survey. I am keeping both just to check them against each other (how much of a difference it makes)
prelim.data$Outcome.Class <- prelim.data$Outcome.Class %>% factor() %>% relevel(ref="Indirect")
prelim.data$Enforced.Monogamy <- prelim.data$Enforced.Monogamy %>% factor() %>% relevel(ref="NO")
prelim.data$Pre.cop <- prelim.data$Pre.cop %>% factor() %>% relevel(ref="0")
prelim.data$Post.cop <- prelim.data$Post.cop %>% factor() %>% relevel(ref="0")
prelim.data$Ratio.Category <- prelim.data$Ratio.Category %>% factor() %>% relevel(ref="Low")
prelim.data$Density.Category <- prelim.data$Density.Category %>% factor() %>% relevel(ref="Low")
prelim.data$SSS.Categorical <- prelim.data$SSS.Categorical %>% factor() %>% relevel(ref="Low")
prelim.data$Blinding <- prelim.data$Blinding %>% factor()

prelim.data %>% pander(split.cell = 40, split.table = Inf)
```

@@

**Ratio Category**: A three level category for the ratio of males to females (high, medium, low).

**Density Category**: A three level category for the density of males to females (high, medium, low).

**SSS.Categorical**: A three level category for the **density & the ratio** of males to females (high medium, low).

**Post cop and Pre cop**: Whether a study allowed Pre/Post-copulatory sexual selection (1) or not (0)
**Blind**: Whether the study was blind or not
**Generations** The number of generations run before fitness outcomes were measured
**Enforced Monogamy**: Whether the study had the low sexual selection treatment as enforced monogamy (YES) or not (NO). Not all studies compared enforced monogamy and SS+ treatments. Some used FB vs MB, where FB is the SS (low intensity). 
**Sex**: Whether the fitness outcome was measured for females (F), males (M) or both (B). Studies that reported 'both' would pool results from males and females.
**Ambiguous**: Is the fitness outcome ambiguous (YES) or not ambigous (NO). Ambiguous outcomes may be those that may not necessarily be directional, that is to say they may be a life history trait. 
**Outcome Class**: Grouped as Direct, Indirect or Ambiguous.
**Environment**: In the methods of the papers included in this study it was usually stated whether additional modifications to the experimental lines were made. Briefly, this was usually a modification that made conditions more stressful such as using a novel food source or elevated mutation load, the effect sizes from these experimental lines are labelled as 'Stressed'. If it was clearly stated that there was no such modification it is labelled 'Unstressed'. However, sometimes the paper was ambiguous in what lines had added stress or the results from stressed and unstressed lines were pooled together, in this case we label it as 'Not Stated'. 
**g**: Hedge's g calculated using the compute.es package
**var.g**: The within study variance associated with the effect size, g
**mean/sd/n.low/high**: The means, standard deviation and sample size for the low or high sexual selection treatments, used to calculate lnCVR (meta-analysis of variance). Rows without these values had hedges g' derived from summary statistics (F, z, chi-square etc.)
**JIF**: Journal Impact factor at year of publication. Several impact factors were unable to be determined/found and are NA.

@@

**Table S3:** Table of effect sizes included in our meta-analysis. See the text following the table for an explanation of each column.
 <br/><br/> 
<input type=button class=hideshow></input>
```{r message=FALSE}
n.blind.ones <- (sum(prelim.data$Blind == "Blind"))
prelim.data %>% 
  summarise(
    Effect_sizes_.Totalq = n(), 
    Publications = prelim.data$Study.ID %>% unique() %>% length(),
    Blind_experiments = n.blind.ones,
    Effect_sizes_.Stressedq = (sum(prelim.data$Environment == "Stressed")),
    Effect_sizes_.Unstressedq = (sum(prelim.data$Environment == "Unstressed")),         
    Effect_sizes_.Maleq = (sum(prelim.data$Sex == "M")),
    Effect_sizes_.Femaleq = (sum(prelim.data$Sex == "F")),
    Effect_sizes_.Both_sexesq = (sum(prelim.data$Sex == "B")),
    Different_species =  prelim.data$Species %>% unique() %>% length(),
    Effect_sizes_.Beetleq = sum(Taxon == "Beetle"),
    Effect_sizes_.Flyq = sum(Taxon == "Fly"),
    Effect_sizes_.Mouseq = sum(Taxon == "Mouse"),
    Effect_sizes_.Nematodeq = sum(Taxon == "Nematode"),
    Effect_sizes_.Miteq = sum(Taxon == "Mite"),
    Effect_sizes_.Cricketq = sum(Taxon == "Cricket"),
    Effect_sizes_.Guppyq = sum(Taxon == "Guppy")) %>% melt() %>%
  mutate(variable = gsub("_", " ", variable),
         variable = gsub("[.]", "(", variable),
         variable = gsub("q", ")", variable)) %>% 
  rename_("n" = "value", " " = "variable") %>% 
  pander(split.cell = 40, split.table = Inf)
```

@@

```{r, fig.height=25, fig.width=10}
# Run standard random effects model
forest.model <- rma(g, var.g, mods = ~ 1, method = "REML", data = prelim.data)

# Obtain residuals
resstandards <- (rstandard.rma.uni(forest.model, type="response"))

# Obtain grand mean effect size    <- ADDED BY LUKE
grand.mean <- as.numeric(forest.model$b)

# Create new df with residuals replacing raw
df.forest.model <- prelim.data                     # <- Luke says: you could just use prelim.data itself, not the residuals?
df.forest.model$g <- resstandards$resid + grand.mean   # <- ADDED BY LUKE
df.forest.model$sei <- resstandards$se

# Create new factor to order factors in a way where Ambig, Indirect and Direct are Grouped
df.forest.model$Outcome_f = factor(df.forest.model$Outcome, levels = c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success'))

# define upper and lower bounds
df.forest.model$lowerci <- df.forest.model$g - 1.96*((df.forest.model$sei))
df.forest.model$upperci <- df.forest.model$g + 1.96*((df.forest.model$sei))

# Get author and year in one
short.author.names <- data.frame(long = df.forest.model$Authors %>% unique(),
                                 short = df.forest.model$Authors %>% unique() %>% 
  as.character() %>% 
  strsplit(split = ",") %>% 
  sapply(FUN=function(x) x[1])) %>%
  left_join(df.forest.model %>% select(Authors, Year) %>% distinct(), by = c("long" = "Authors")) %>%
  mutate(suffix = "")

@@

# Add the AuthorYear column to the dataframe of effect sizes
short.author.names <- short.author.names %>%
  mutate(AuthorYear = paste(short, " ", Year, suffix, sep="")) %>%
  select(long, AuthorYear)
df.forest.model <- df.forest.model %>% 
  left_join(short.author.names, by = c("Authors" = "long"))

#Generate a plot
p.meta <- df.forest.model %>% 
  mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
         Sex = replace(Sex, Sex == "M", "Male"),
         Sex = replace(Sex, Sex == "F", "Female")) %>%
  ggplot(aes(y=reorder(AuthorYear, -g), x = g, shape = Sex, color = Outcome.Class)) +
  geom_errorbarh(aes(xmin = lowerci, xmax = upperci), height = 0.1) +
  geom_point(size = 2) +  #Add data points and color them black
  scale_x_continuous(limits=c(-5, 5), name='Standardized Mean Difference (g)') +
  scale_color_discrete(name = "Relationship\nto fitness") + 
  ylab('Reference') + 
  geom_vline(xintercept=0, color='black', linetype='dashed')+
  facet_grid(Outcome_f~., scales= 'free', space='free')+
  theme(strip.text.y = element_text(angle = 0))
ggsave(plot = p.meta, filename = "figures/Big_forest_plot.eps", height = 25, width = 12)
p.meta
```
<br></br>
**Figure 1:** Forest plot of effect sizes and their 95% confidence intervals, grouped according to environment (stressed or unstressed) and the sex of the individuals whose fitness trait was measured (male, female, or both sexes mixed together). Rows with multiple data points denote studies that provided multiple effect sizes.

@@

>The following documents how I could run individual models for each outcome or outcome.class of interest and then plot them. This may be good to add to the above forest plot (in the form of a polygon; how many studies report their estimates) but at the same time, it just adds results from different subsetted models rather than one combined one (as we use when investigating sex and environment)

> Nice idea, but I think the correct way to do this is to fit Outcome.class as a moderator, and then use predict() to find the average effect size within each of the 3 levels, as you have done below. I coded something below, but it's wrong:

```{r}
model.outcome.class <- rma(g, var.g,
                           mods = ~ Outcome.Class, 
                           method = "REML", 
                           intercept = TRUE, 
                           data = prelim.data)

# Get the intercept (i.e. the grand mean for 'ambiguous', and the effects for the others)
mod.table <- do.call("cbind", model.outcome.class[names(model.outcome.class) %in% c("b", "ci.lb", "ci.ub")])

data.frame(Outcome.class = c("Ambiguous", "Direct", "Indirect"),
           mod.table) %>%
  ggplot(aes(y = Outcome.class, x = V1))  +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_errorbarh(aes(xmin = ci.lb, xmax = ci.ub), height=0) +
  geom_point() + 
  xlab("Effect size and 95% CIs")
```

@@

From the previous forest plot and models we see that overall sexual selection is beneficial towards population fitness. Although this is heavily modulated by the individual outcome and the outcome class. We explore heterogeneity in more depth later in this document.

@@

### Effect size differs between taxa

First run the model using a restricted dataset where we remove effect sizes with Ambiguous outcomes or environments that were not stated whether they were stressed or unstressed. In this model we use Sex, Environment, Taxon and the interaction between sex and environment as we hypothesise that the a stressful enviornment may be of greater importance to the female sex due to 'female demographic dominance', which essentially states that female fitness is more important to the overall population demographics and that most benefits or conversely costs will accrue to female fitness components.

```{r}
restricted.data <- prelim.data %>% 
  filter(Outcome.Class != "Ambiguous" & Environment != "Not Stated") %>% 
  mutate(Sex = as.character(Sex), 
         Environment = as.character(Environment), 
         Outcome.Class.2 = as.character(Outcome.Class), 
         Enforced.Monogamy = as.character(Enforced.Monogamy))

# Make sure the factors are leveled in the same order as we write our prediction function (below)
restricted.data$Environment <- restricted.data$Environment %>% factor() %>% relevel(ref="Unstressed")
restricted.data$Sex <- restricted.data$Sex %>% factor() %>% relevel(ref="M")
restricted.data$Outcome.Class <- restricted.data$Outcome.Class %>% factor() %>% relevel(ref="Indirect")
restricted.data$Taxon <- relevel(restricted.data$Taxon, ref = "Mouse")

model.complete <- rma.mv(g, var.g, 
                         mods = ~ 1 + Sex * Environment, # << ----- Add big model, then cull predictors to this one
                         random = list(~ 1 | Study.ID, 
                                       ~ 1 | Outcome), 
                         method = "REML", 
                         data = restricted.data)

@@

  predict(model.complete, newmods=c(B, F, Stressed, Cricket, Fly, Guppy, Mite, Mouse, interaction1=interaction1, interaction2=interaction2))
}
# Get the predictions for each combination of moderators
predictions.complete <- as.data.frame(expand.grid(Sex = c("M", "B", "F"),
                           Environment = c("Unstressed", "Stressed"),
                           Taxon = c("Cricket", "Fly", "Guppy", "Mite", "Mouse")))
predictions.complete <- cbind(predictions.complete, do.call("rbind", apply(predictions.complete, 1, get.predictions.complete))) %>%
  select(Sex, Environment, Taxon, pred, se, ci.lb, ci.ub) 
for(i in 4:7) predictions.complete[,i] <- unlist(predictions.complete[,i])
```

Third, plot the model predictions for effect size (Hedges' g) for male, female and both sexes under both stressed and unstressed condition and faceted for each taxon.

> I would like to know how to join a table with mean, and CI values to the forest plots I am generating.

> You can make tables with ggplot, and bind them to graphs using the grid and gridExtra packages. It's pretty hard! See ?gridExtra::tableGrob. 
> Honestly might be easier to do it manually with e.g. Inkscape or Illustrator.

```{r, fig.height= 7, fig.width=10}
pd <- position_dodgev(height = .7)
predictions.complete %>% ggplot(aes(x = pred, y= Environment, colour = Sex)) + 
  geom_vline(xintercept = 0, linetype = 2, colour = "grey70") + 
  geom_errorbarh(aes(xmin = predictions.complete$ci.lb, xmax = predictions.complete$ci.ub), height = 0, position = pd) +
  geom_point(position = pd, size=2) + 
  facet_grid(Taxon ~.)+
  ylab("Environment")+
  xlab("Model Prediction (Hedges g)")+
  xlim(-2, 2)+
  ggtitle('Effects of Sex, Stress and Outcome Class \non Population Fitness for Each Taxon')
```

This model indicates quite a bit of heterogeneity between taxon. More so that that confidence limits increase, rather than radically changing direction of effect. However we can see from this that under stressed environments, females tend to

@@

```{r}
#run model without taxon: 3 level model with outcomes within a study
model.complete2 <- rma.mv(g, var.g, 
                          mods = ~ 1 + Sex + Environment + Sex:Environment, 
                          random = ~ 1 | Study.ID/Outcome, 
                          method = "REML", 
                          data = restricted.data)
summary(model.complete2)
```

```{r, fig.height= 7, fig.width=10}

@@

pd <- position_dodgev(height = .5)
predictions.complete2 %>% ggplot(aes(x = pred, y= Environment, colour = Sex)) + 
  geom_vline(xintercept = 0, linetype = 2, colour = "grey70") + 
  geom_errorbarh(aes(xmin = predictions.complete2$ci.lb, xmax = predictions.complete2$ci.ub), height = 0, position = pd) +
  geom_point(position = pd) + 
  ylab("Environment")+
  xlab("Effect Size (Hedges g)")+
  xlim(-.75, .75)+
  ggtitle('Effects of Sex, Stress \non Population Fitness')
```

We see that female fitness in stressed environments is greater than the other measurements. For outcomes that were measured for both female and males we see a greater uncertainty in the estimate. It is not obviously clear why this is. The 'both' outcomes are restricted to extinction rate, offspring viability, mutant frequency and reproductive success. However, the shift from 'both' being ns in unstressed to significant in stressed may reflect the dampening of the negative correlations (sexual antagonism).

```{r}
table(restricted.data$Outcome, restricted.data$Sex)
```

@@

#### Multilevel model using metafors alternative random effect structure

>>>>

```{r warning=FALSE, message=FALSE, results='hide'}
library(knitr)
library(pander)
library(compute.es)
library(metafor)
library(dplyr)
library(lme4)
library(forestplot)
library(ggplot2)
library(kableExtra)
library(MuMIn)
library(glmulti)
library(cowplot)
library(ggrepel)
library(reshape2)
library(RColorBrewer)
source("Vdodge_function.R") # nice function for ggplot
```

@@

**Table S1:** An eligibility criteria was based on four features a study needed to include (discussed above), to be eligable for inclusion in the meta-analysis the study needed to satisfy all criteria. Here we applied a step-wise process to the studies that had their full-text read and excluded them when they first failed to meet the criteria. Additional notes documenting reasons behind exclusion were also taken.
 <br/><br/> 
<input type=button class=hideshow></input>
```{r}
Eligibility.criteria <- read.csv('data/Eligibility Workbook(22.02).csv', 
                                 fileEncoding="UTF-8")
kable(Eligibility.criteria, "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "500px")
```

@@

**Table S2:** Table of effect sizes included in our meta-analysis. See the text following the table for an explanation of each column.
 <br/><br/> 
<input type=button class=hideshow></input>
```{r}
# Load the data and clean up the variable formats
prelim.data <- read.csv('data/Preliminary data frame 22.2.18.csv')
prelim.data$Study.ID <- prelim.data$Study.ID %>% factor()
prelim.data$Taxon <- prelim.data$Taxon %>% factor()
prelim.data$Group.ID <- prelim.data$Group.ID %>% factor()
prelim.data$Authors <- prelim.data$Authors %>% factor()
prelim.data$Environment <- prelim.data$Environment %>% factor %>% relevel(ref="Unstressed")
prelim.data$Sex <- prelim.data$Sex %>% factor %>% relevel(ref="B")
prelim.data$Ambiguous <- prelim.data$Ambiguous %>% factor()
prelim.data$Species <- prelim.data$Species %>% factor()
#Outcome.Class.2 is using the categories that were decided by survey. I am keeping both just to check them against each other (how much of a difference it makes)
prelim.data$Outcome.Class <- prelim.data$Outcome.Class %>% factor() %>% relevel(ref="Indirect")
prelim.data$Enforced.Monogamy <- prelim.data$Enforced.Monogamy %>% factor() %>% relevel(ref="NO")
prelim.data$Pre.cop <- prelim.data$Pre.cop %>% factor() %>% relevel(ref="0")
prelim.data$Post.cop <- prelim.data$Post.cop %>% factor() %>% relevel(ref="0")
prelim.data$Blinding <- prelim.data$Blinding %>% factor()

kable(prelim.data, "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "500px")
```

@@

**Post cop and Pre cop**: Whether a study allowed Pre/Post-copulatory sexual selection (1) or not (0)

**Blind**: Whether the study was blind or not

**Generations** The number of generations run before fitness outcomes were measured

**Enforced Monogamy**: Whether the study had the low sexual selection treatment as enforced monogamy (YES) or not (NO). Not all studies compared enforced monogamy and SS+ treatments. Some used FB vs MB, where FB is the SS (low intensity).

**Sex**: Whether the fitness outcome was measured for females (F), males (M) or both (B). Studies that reported 'both' would pool results from males and females.

**Ambiguous**: Is the fitness outcome ambiguous (YES) or not ambigous (NO). Ambiguous outcomes may be those that may not necessarily be directional, that is to say they may be a life history trait.

**Outcome Class**: Grouped as Direct, Indirect or Ambiguous.

**Environment**: In the methods of the papers included in this study it was usually stated whether additional modifications to the experimental lines were made. Briefly, this was usually a modification that made conditions more stressful such as using a novel food source or elevated mutation load, the effect sizes from these experimental lines are labelled as 'Stressed'. If it was clearly stated that there was no such modification it is labelled 'Unstressed'. However, sometimes the paper was ambiguous in what lines had added stress or the results from stressed and unstressed lines were pooled together, in this case we label it as 'Not Stated'.

**g**: Hedge's g calculated using the compute.es package.

**var.g**: The within study variance associated with the effect size, g.

**mean/sd/n.low/high**: The means, standard deviation and sample size for the low or high sexual selection treatments, used to calculate lnCVR (meta-analysis of variance). Rows without these values had hedges g' derived from summary statistics (F, z, chi-square etc.).

**JIF**: Journal Impact factor at year of publication. Several impact factors were unable to be determined/found and are NA.

@@

**Table S3:** Table of effect sizes included in our meta-analysis. See the text following the data table for an explanation of each column.
 <br/><br/> 
<input type=button class=hideshow></input>
```{r message=FALSE}
n.blind.ones <- (sum(prelim.data$Blind == "Blind"))
prelim.data %>% 
  summarise(
    Effect_sizes_.Totalq = n(), 
    Publications = prelim.data$Study.ID %>% unique() %>% length(),
    Blind_experiments = n.blind.ones,
    Effect_sizes_.Stressedq = (sum(prelim.data$Environment == "Stressed")),
    Effect_sizes_.Unstressedq = (sum(prelim.data$Environment == "Unstressed")),         
    Effect_sizes_.Maleq = (sum(prelim.data$Sex == "M")),
    Effect_sizes_.Femaleq = (sum(prelim.data$Sex == "F")),
    Effect_sizes_.Both_sexesq = (sum(prelim.data$Sex == "B")),
    Different_species =  prelim.data$Species %>% unique() %>% length(),
    Effect_sizes_.Beetleq = sum(Taxon == "Beetle"),
    Effect_sizes_.Flyq = sum(Taxon == "Fly"),
    Effect_sizes_.Mouseq = sum(Taxon == "Mouse"),
    Effect_sizes_.Nematodeq = sum(Taxon == "Nematode"),
    Effect_sizes_.Miteq = sum(Taxon == "Mite"),
    Effect_sizes_.Cricketq = sum(Taxon == "Cricket"),
    Effect_sizes_.Guppyq = sum(Taxon == "Guppy")) %>% melt() %>%
  mutate(variable = gsub("_", " ", variable),
         variable = gsub("[.]", "(", variable),
         variable = gsub("q", ")", variable)) %>% 
  rename_("n" = "value", " " = "variable") %>% 
  pander(split.cell = 40, split.table = Inf)
```
 <br/><br/> 
**Table S4:** Table of fitness outcomes included in our meta-analysis by sex.
 <br/><br/> 
<input type=button class=hideshow></input>
```{r}
Outcome_and_sex <- table(prelim.data$Outcome, prelim.data$Sex) %>%
  pander(split.cell = 40, split.table = Inf)
```

@@

```{r, fig.height=25, fig.width=10}
# Run standard random effects model
# forest.model <- rma.mv(g, var.g, 
#                        mods = ~ 1 + Sex * Environment + Taxon,
#                        random = list(~ 1 | Study.ID, 
#                                        ~ 1 | Outcome),
#                        method = "REML", 
#                        data = prelim.data)
# 
# # Obtain residuals
# resstandards <- (rstandard.rma.mv(forest.model, 
#                                    type="response"))
# 
# # Obtain grand mean effect size    <- ADDED BY LUKE
# grand.mean <- as.numeric(forest.model$b)
# 
# # Create new df with residuals replacing raw
# df.forest.model <- prelim.data                     # <- Luke says: you could just use prelim.data itself, not the residuals?
# df.forest.model$g <- resstandards$resid + grand.mean   # <- ADDED BY LUKE
# df.forest.model$sei <- resstandards$se

# Create new factor to order factors in a way where Ambig, Indirect and Direct are Grouped
prelim.data$Outcome_f = factor(prelim.data$Outcome, levels = c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success'))

# define upper and lower bounds
prelim.data$lowerci <- prelim.data$g - 1.96*(sqrt(prelim.data$var.g))
prelim.data$upperci <- prelim.data$g + 1.96*(sqrt(prelim.data$var.g))

# Get author and year in one
short.author.names <- data.frame(long = prelim.data$Authors %>% unique(),
                                 short = prelim.data$Authors %>% unique() %>% 
  as.character() %>% 
  strsplit(split = ",") %>% 
  sapply(FUN=function(x) x[1])) %>%
  left_join(prelim.data %>% select(Authors, Year) %>% distinct(), by = c("long" = "Authors")) %>%
  mutate(suffix = "")

@@

# Add the AuthorYear column to the dataframe of effect sizes
short.author.names <- short.author.names %>%
  mutate(AuthorYear = paste(short, " ", Year, suffix, sep="")) %>%
  select(long, AuthorYear)
prelim.data <- prelim.data %>% 
  left_join(short.author.names, by = c("Authors" = "long"))

#Generate a plot
p.meta <- prelim.data %>% 
  mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
         Sex = replace(Sex, Sex == "M", "Male"),
         Sex = replace(Sex, Sex == "F", "Female")) %>%
  ggplot(aes(y=reorder(AuthorYear, -g), x = g, shape = Sex, color = Outcome.Class)) +
  geom_errorbarh(aes(xmin = lowerci, 
                     xmax = upperci), height = 0.1) +
  geom_point(size = 3) +  #Add data points and color them black
  scale_x_continuous(limits=c(-5, 5), name='Standardized Mean Difference (g)') +
  scale_color_discrete(name = "Relationship\nto fitness") + 
  ylab('Reference') + 
  geom_vline(xintercept=0, color='black', linetype='dashed')+
  facet_grid(Outcome_f~., scales= 'free', space='free')+
  theme(strip.text.y = element_text(angle = 0))+
ggsave(plot = p.meta, filename = "figures/Big_forest_plot.eps", height = 25, width = 12)
p.meta
```
<br></br>
**Figure 1:** Forest plot of raw effect sizes and their 95% confidence intervals, grouped according to environment (stressed or unstressed) and the sex of the individuals whose fitness trait was measured (male, female, or both sexes mixed together). Rows with multiple data points denote studies that provided multiple effect sizes.

@@

> Let's just run one big model then cull from there

<!-- >The following documents how I could run individual models for each outcome or outcome.class of interest and then plot them. This may be good to add to the above forest plot (in the form of a polygon; how many studies report their estimates) but at the same time, it just adds results from different subsetted models rather than one combined one (as we use when investigating sex and environment) -->

<!-- > Nice idea, but I think the correct way to do this is to fit Outcome.class as a moderator, and then use predict() to find the average effect size within each of the 3 levels, as you have done below. I coded something below, but it's wrong: -->

<!-- ```{r} -->
<!-- model.outcome.class <- rma(g, var.g, -->
<!--                            mods = ~ Outcome.Class,  -->
<!--                            method = "REML",  -->
<!--                            intercept = TRUE,  -->
<!--                            data = prelim.data) -->

<!-- # Get the intercept (i.e. the grand mean for 'ambiguous', and the effects for the others) -->
<!-- mod.table <- do.call("cbind", model.outcome.class[names(model.outcome.class) %in% c("b", "ci.lb", "ci.ub")]) -->

<!-- data.frame(Outcome.class = c("Ambiguous", "Direct", "Indirect"), -->
<!--            mod.table) %>% -->
<!--   ggplot(aes(y = Outcome.class, x = V1))  + -->
<!--   geom_vline(xintercept = 0, linetype = 2) + -->
<!--   geom_errorbarh(aes(xmin = ci.lb, xmax = ci.ub), height=0) + -->
<!--   geom_point() +  -->
<!--   xlab("Effect size and 95% CIs") -->
<!-- ``` -->

@@

<!-- From the previous forest plot and models we see that overall sexual selection is beneficial towards population fitness. Although this is heavily modulated by the individual outcome and the outcome class. We explore heterogeneity in more depth later in this document.  -->

### Exploring our data with the large set of covariates

We collected data from fitness components that were deemed ambiguous as well as unambiguous. The ambiguous outcomes are likely to add in heterogeneity to the models and not help us in answering questions of fitness effects of sexual selection. A model utilising our complete dataset with many moderator variables would thus be:

```{r}
model.preliminary <- rma.mv(g, var.g, 
                         mods = ~ 1 + Sex * Environment + Taxon + Outcome.Class + Generations + Blinding, # << ----- Add big model, then cull predictors to this one
                         random = list(~ 1 | Study.ID, 
                                       ~ 1 | Outcome), 
                         method = "REML", 
                         data = prelim.data)

summary(model.preliminary)

```
<br></br>
**A note on random effects** Here we utilise crossed random effects of Study.ID and Outcome. Nesting Outcomes within Study.ID can also be achieved through ``random = ~ 1 | Study.ID/Outcome``. However given that the same outcome is expected to be measured in the same/very similar way between studies we used a crossed random effects design.

From this model we can see that there are several redundant moderators: Blinding, Generations and the Outcome class (direct, indirect and ambiguous) show little effect and are not key to our research question (like sex and environment are). However, because taxa is a likely source of heterogeneity and effect size could reasonably be expected to differ between taxa, we investigate this fixed effect further...

@@

### Effect size differ slightly between taxa

First we want to run the model using a restricted dataset where we remove effect sizes with Ambiguous outcomes or environments that were not stated whether they were stressed or unstressed (confusing and confounding). In this model we use Sex, Environment, Taxon and the interaction between sex and environment as we hypothesise that the a stressful enviornment may be of greater importance to the female sex due to 'female demographic dominance', which essentially states that female fitness is more important to the overall population demographics and that most benefits or conversely costs will accrue to female fitness components.

```{r}
#Restrict the dataset for unambiguous outcomes and environments 
restricted.data <- prelim.data %>% 
  filter(Outcome.Class != "Ambiguous" & Environment != "Not Stated") %>% 
  mutate(Sex = as.character(Sex), 
         Environment = as.character(Environment), 
         Outcome.Class.2 = as.character(Outcome.Class), 
         Enforced.Monogamy = as.character(Enforced.Monogamy))

# Make sure the factors are leveled in the same order as we write our prediction function (below)
restricted.data$Environment <- restricted.data$Environment %>% factor() %>% relevel(ref="Unstressed")
restricted.data$Sex <- restricted.data$Sex %>% factor() %>% relevel(ref="M")
restricted.data$Outcome.Class <- restricted.data$Outcome.Class %>% factor() %>% relevel(ref="Indirect")
restricted.data$Taxon <- relevel(restricted.data$Taxon, ref = "Beetle")

model.complete <- rma.mv(g, var.g, 
                         mods = ~ 1 + Sex * Environment + Taxon, # << ----- Add big model, then cull predictors to this one
                         random = list(~ 1 | Study.ID, 
                                       ~ 1 | Outcome), 
                         method = "REML", 
                         data = restricted.data)

@@

  predict(model.complete, newmods=c(B, F, Stressed, Cricket, Fly, Guppy, Mite, Mouse, interaction1=interaction1, interaction2=interaction2))
}
# Get the predictions for each combination of moderators
predictions.complete <- as.data.frame(expand.grid(Sex = c("M", "B", "F"),
                           Environment = c("Unstressed", "Stressed"),
                           Taxon = c("Beetle", "Cricket", "Fly", "Guppy", "Mite", "Mouse")))
predictions.complete <- cbind(predictions.complete, do.call("rbind", apply(predictions.complete, 1, get.predictions.complete))) %>%
  select(Sex, Environment, Taxon, pred, se, ci.lb, ci.ub) 
for(i in 4:7) predictions.complete[,i] <- unlist(predictions.complete[,i])
```

Thirdly, plot the model predictions for effect size (Hedges' g) for male, female and both sexes under both stressed and unstressed condition and faceted for each taxon.

<!-- > I would like to know how to join a table with mean, and CI values to the forest plots I am generating. -->

<!-- > You can make tables with ggplot, and bind them to graphs using the grid and gridExtra packages. It's pretty hard! See ?gridExtra::tableGrob.  -->
<!-- > Honestly might be easier to do it manually with e.g. Inkscape or Illustrator.	 -->

```{r, fig.height= 5, fig.width=7.5}
pd <- position_dodgev(height = .7)
Taxon.metaanlysis <- predictions.complete %>% ggplot(aes(x = pred, 
                                                         y= Environment, 
                                                         fill = Sex)) + 
  geom_vline(xintercept = 0, linetype = 2, colour = "grey70") + 
  geom_errorbarh(aes(xmin = predictions.complete$ci.lb, 
                     xmax = predictions.complete$ci.ub,
                     color= Sex), 
                 height = 0, position = pd) +
  geom_point(position = pd, size=3, shape=21, color = "grey20") + 
  facet_grid(Taxon ~.)+
  ylab("Environment \n")+
  xlab("\nModel Prediction (Hedges g)")+
  xlim(-2, 2)+
  ggtitle('Effects of Sex, Stress and Outcome Class \non Population Fitness for Each Taxon')+
  scale_fill_brewer(palette = "Set1")+
  scale_color_brewer(palette = "Set1")

ggsave(plot = Taxon.metaanlysis, filename = "figures/Taxon_metaanalysis_plot.eps", height = 5, width = 7.5)
Taxon.metaanlysis
```

This model indicates quite a bit of heterogeneity between taxon. However, more striking is that confidence bands increase for taxa with low sample size. As previously shown, the beetle and fly taxa are the most heavily sampled and in the above figure have the narrowest confidence bands. The overall direction of effect does not change, although guppies and mice show effect sizes ~ 0. We can see from this that under stressed environments, females from all taxa appear to have greater fitness increase than males or 'both'.

@@

```{r}
#run model without taxon: same random effects as above
model.complete2 <- rma.mv(g, var.g, 
                          mods = ~ 1 + Sex + Environment + Sex:Environment, 
                          random = list(~ 1 | Study.ID, 
                                       ~ 1 | Outcome), 
                          method = "REML", 
                          data = restricted.data)
summary(model.complete2)
```

```{r, fig.height= 5, fig.width=7.5}

@@

#And plot the results
pd <- position_dodgev(height = .5)
EnvSex.metaanalysis <- predictions.complete2 %>% ggplot(aes(x = pred, y= Environment, fill = Sex)) + 
  geom_vline(xintercept = 0, linetype = 2, colour = "grey70") + 
  geom_errorbarh(aes(xmin = predictions.complete2$ci.lb, 
                     xmax = predictions.complete2$ci.ub,
                     color = Sex), height = 0, position = pd) +
  geom_point(position = pd, size=3, shape=21, color = "grey20") + 
  ylab("Environment\n")+
  xlab("\nEffect Size (Hedges g)")+
  xlim(-.75, .75)+
  ggtitle('Effects of Sex, Stress \non Population Fitness')+
  scale_fill_brewer(palette = "Set1")+
  scale_color_brewer(palette = "Set1")

ggsave(plot = EnvSex.metaanalysis, filename = "figures/Environment_Sex_metaanalysis_plot.eps", height = 5, width = 7.5)
EnvSex.metaanalysis
```

We see that female fitness in stressed environments is greater than the other measurements. For outcomes that were measured for both female and males we see a greater uncertainty in the estimate. It is not obviously clear why this is. The 'both' outcomes are restricted to extinction rate, offspring viability, mutant frequency and reproductive success. However, the shift from 'both' being not significant in unstressed to significant in stressed may reflect the dampening of the negative correlations (sexual antagonism).

@@

<!-- #### Multilevel model using metafors alternative random effect structure  -->
